---
title: "IPE&2_myanalysis"
author: "Bruce Peng"
date: "3 April 2019"
output: html_document
---
This contains analysis of IPE, in essense we conducted a replication Of Gaesser and Schacter (2014) imagine helping experiment. Specifically, we replicated the protocol for study 2 in that study in a NZ sample. 

**Participants and trial numbers:**
A total of 40 participants are included in this dataset, each participants completed 30 trials thus the total number of trials is 40x30= 1200. 32 trials were deleted due to written description not matching the condition requirement or other issues. Thus, the total number of trials = 1168.


**Data description:**
*Participant:* N=40 following the format of IPE1XX for version 1 of the study (see below), IPE21XX indicates participants in version 2. 
*Story_ID:* Story presented to participants on each trial, a total of 30 stories were presented. These stories can be found in IPE_stimuli.xlsx
*Trial:* Trial order presented to participant.
*Condition:* Imagine helping (Experimental:Imagine),Estimate helping (Control:Estimate) and identify journalistic technique (Control:Identify)*
*Version:* Version 1 is a direct replication of Gaesser et al 2014 design where written description and ratings were collected after all simulation trials, version 2 shifts the ratings and written responses to the end of each simulation trial. 
*Gender:* 0-male, 1-female
*Perspective.response:*  When you identified the media website, imagined helping, or visualized the media website and comments  did you consider  the thoughts and feelings of the person? (collected for all conditions). Responses are made on a 1(not at all)- 7 (strongly considered). 
*Detail.response:* The imagined media website/scene in your mind was? (collected for estimate and imagine helping conditions). Responses were made on a 1(simple)-7(detailed) Likert scale. 
*Coherence.response:*The imagined media website/scene in your mind was? (collected for estimate and imagine helping conditions). Responses were made on a 1(vague)-7(coherent and clear) Likert scale. 
*Preliving.response:* How strongly did you experience the imagined event in your mind? (collected for imagine helping conditions). Responses were made on a 1(not at all)-7(vividly) Likert scale. 
*Help.response:* Main DV of interest. How likely would you be to help in this situation? (collected for all conditions). Responses are made on a 1(not at all)- 7 (very willing).

*Emotional reaction:*
Emotional reaction (collected for all conditions) rated on a 1(not at all)-7(very strongly) Likert scale for the following emotions:
-	Intrigued
-	Soft-hearted
-	Troubled 
-	Warm 
-	Distressed
-	Sympathetic
-	Intent
-	Compassionate
-	Disturbed
-	Tender
-	Moved
-	Worried
Note emotional concern refers to 6 measures (i.e. sympathy, compassion, moved, tendered, soft-hearted and warm), the 12 measures were used to mask these 6 measures to minimize participants’ awareness of the emotional concern measures. 

#Package and directory set up
```{r, include=FALSE}
#Obtain necessary packages
if (!require(sjstats)) install.packages('sjstats')
if (!require(sjPlot)) install.packages('sjPlot')
#if (!require(sjmisc)) install.packages('sjmisc')
if (!require(lme4)) install.packages('lme4')
if (!require(lmerTest)) install.packages('lmerTest')
if (!require(lattice)) install.packages('lattice')
if (!require(mediation)) install.packages('mediation')
if (!require(ggeffects)) install.packages('ggeffects')
if (!require(emmeans)) install.packages('emmeans')
if (!require(lavaan)) install.packages('lavaan')
if (!require(simr)) install.packages('simr')
if (!require(reshape)) install.packages('reshape')
if (!require(tidyverse)) install.packages('tidyverse')
if (!require(MuMIn)) install.packages('MuMIn')
```

```{r setup, include=FALSE}
#Load packages
library(sjstats)
library (MuMIn)
library(sjPlot)
library(sjmisc)
library (lme4)
library(lmerTest)
library (lattice)
library (mediation)
library (emmeans)
library(ggeffects)
library(lavaan)
library(simr)
library(reshape)
library (tidyverse)
#set working directory
setwd('G:/My Drive/Phd (1)/Experiment/Studies/Data/IPE/IPE_replication/IPE_2_analysis/')
setwd('C:/Users/Bruce Peng/Google Drive/Phd (1)/Experiment/Studies/Data/IPE/IPE_replication/IPE_2_analysis/')
#source custom functions
source("source/group_center.R")
source("source/Plot_LMM.R")
source("source/means.R")
source('http://faculty.missouri.edu/huangf/data/mcfa/mcfa.R')
```

#Data 
*Loading data 
```{r}
IPE.df<- read.csv('IPE&2_fullData_N=40.csv', header=T)
IPE.df<- IPE.df[complete.cases(IPE.df$Condition),]
IPE.df$Story_ID<- as.factor(IPE.df$Story_ID)
IPE.df$Condition<- as.factor(IPE.df$Condition)
IPE.df$Condition<- relevel(IPE.df$Condition,ref='Identify')
```

*Data setup
```{r}
IPE.df<- IPE.df%>% 
              mutate(
                #Create dummy variables
                dummy_ident=as.numeric(Condition=='Identify'),
                dummy_img= as.numeric(Condition=='Imagine'),
                dummy_est= as.numeric(Condition=='Estimate'),
                #Create scene imagery measure
                Scene=(Coherence.response+Detail.response)/2,        
                #Within-cluster centering
                Scene_C= group_center(Scene,Participant),
                Coherence_C=group_center(Coherence.response,Participant),
                Detail_C=group_center(Detail.response,Participant),
                Perspective_C =group_center(Perspective.response,Participant))
#Create data file that only include conceptual helping and imagine condition. This is utilizied for interaction analyses (scene imagery*Condition) and multilevel moderated mediation analysis
interaction.df<- IPE.df%>%
                      filter(Condition!='Identify')%>%
                      mutate(Perspective_C =group_center(Perspective.response,Participant))
interaction.df$Condition<- droplevels(interaction.df$Condition)
```


#Main effect analyses: Replication of prosocial simulation effect
##Determine if clustering exists for story ID and participants
```{r}
null_full<- lmer(help.response~(1|Participant)+(1|Story_ID), data=IPE.df)
summary(IPE.df)
ranova(null_full)#significant so should include story and participant as a random effect
```

##Prosoical simulation effect
```{r}
# follow the parsimonious mixed model approach described by Bates 2015 which involve fitting a maximual model first the iteratively reduce random effect dimension to find the best model.
zcp_model<- lmer(help.response~Condition+(dummy_est+dummy_img||Participant)+(dummy_est+dummy_img||Story_ID), data= IPE.df)
step(zcp_model)#suggest that dummy_est and dummy_img  in story_ID should be deleted adopting the 0.2 criteria used in Matuschek et al 2017
zcp_model_rm<- lmer(help.response~Condition+(dummy_img+dummy_est||Participant)+(1|Story_ID), data= IPE.df)

#add in correlation parameter
final_model<- lmer(help.response~Condition+(dummy_img+dummy_est|Participant)+(1|Story_ID), data= IPE.df)
anova(zcp_model_rm,final_model, refit=F)
anova(final_model, test='kenward-roger')
confint(final_model)
```
###Post hoc comparison
```{r}
emmeans(final_model, pairwise~Condition, adjust= 'bonferroni')
```
###Plots
```{r}
#Condition difference in willingness to help
ggpredict(final_model, c('Condition'))%>% plot()

#assess random effect relative to the means random effect
plot_model(final_model, type= 're')

#Identify as reference group
final_model2<- lmer(help.response~dummy_est+dummy_img+(dummy_img+dummy_est|Participant)+(1|Story_ID), data= IPE.df)
Plot_LMM(final_model2, 'Identify', 'Estimate', 'Imagine',1)
Plot_LMM(final_model2, 'Identify', 'Estimate', 'Imagine',2)
Plot_LMM(final_model2, 'Identify', 'Estimate', 'Imagine',3)
Plot_LMM(final_model2, 'Identify', 'Estimate', 'Imagine',4)
#Imagine as reference group
final_model3<- lmer(help.response~dummy_ident+dummy_img+(dummy_img+dummy_ident|Participant)+(1|Story_ID), data= IPE.df)
Plot_LMM(final_model3, 'Estimate', 'Identify', 'Imagine',1)
Plot_LMM(final_model3, 'Estimate', 'Identify', 'Imagine',2)
Plot_LMM(final_model3, 'Estimate', 'Identify', 'Imagine',3)
Plot_LMM(final_model3, 'Estimate', 'Identify', 'Imagine',4)
```
###Assumption testing
```{r}
plot_model(final_model, type='diag')
```
###Effect size
```{r}
r.squaredGLMM(final_model)
```
###Power analysis
```{r}
pcurve_main <- powerCurve(final_model, test=fcompare(help.response~1), along='Participant')
plot(pcurve_main)
```



#Interaction analysis: Condition(estimate vs imagine)* Vividness measures. 
##Detail & Coherence
```{r}
#Detail
int_zcp_det<- lmer (help.response~Condition*Detail_C+(dummy_img*Detail_C||Participant)+ (dummy_img*Detail_C||Story_ID),data= interaction.df)
step(int_zcp_det)# Retain Dummy:Detail_C &dummy_img in partiicpant and Detail_C in storyID
int_rm_det<- lmer (help.response~Condition*Detail_C+(dummy_img+dummy_img:Detail_C||Participant)+(Detail_C||Story_ID),data= interaction.df)
##Final model
int_final_det<- lmer (help.response~Condition*Detail_C+(dummy_img+dummy_img:Detail_C|Participant)+(1|Story_ID),data= interaction.df)
int_final_det<-update(int_final_det, .~., start= getME(int_final_det, 'theta')) #refitted twice and converged
anova(int_rm_det,int_final_det, refit=F)
anova(int_final_det, test='kenward-roger')
summary(int_final_det)

#Coherence
int_zcp_coh<- lmer (help.response~Condition*Coherence_C+(dummy_img*Coherence_C||Participant)+(dummy_img*Coherence_C||Story_ID),data= interaction.df)
step(int_zcp_coh) #Retain coherence_C in storyID and dummy_img in participant
int_rm_coh<- lmer (help.response~Condition*Coherence_C+(dummy_img||Participant)+ (Coherence_C||Story_ID),data= interaction.df)
#add in correlation parameters: one at a time
int_final_coh<- lmer (help.response~Condition*Coherence_C+(dummy_img|Participant)+(Coherence_C|Story_ID),data= interaction.df)
int_final_coh<- update(int_final_coh, .~., start= getME(int_final_coh, 'theta'))#manage to converge after 3 times
anova(int_rm_coh,int_final_coh, refit=F)
anova(int_final_coh, test='kenward-roger')
summary(int_final_coh)
```

###Plot the effect
```{r}
#Detail
sd<-sd(interaction.df$Detail_C);m<-mean(interaction.df$Detail_C)
m-sd;m;m+sd;
ggpredict(int_final_det, c("Condition","Detail_C [-1.53,0,1.53]"))%>% plot()
ggpredict(int_final_det, c("Detail_C[-1.53,0,1.53]","Condition"))%>% plot()
#Coherence
sd<-sd(interaction.df$Coherence_C);m<-mean(interaction.df$Coherence_C)
m-sd;m;m+sd;
ggpredict(int_final_coh, c("Condition","Coherence_C [-1.43,0,1.43]"))%>% plot()
ggpredict(int_final_coh, c("Coherence_C[-1.43,0,1.43]","Condition"))%>% plot()
```
###Assumption testing
```{r}
#Detail
plot_model(int_final_det, type='re')
plot_model(int_final_det, type='diag')
#Coherence
plot_model(int_final_coh, type='re')
plot_model(int_final_coh, type='diag')
```

###Effect size calculation
```{r}
#Detail
r.squaredGLMM(int_final_det)
#Coherence
r.squaredGLMM(int_final_coh)
```
###Power analysis
```{r}
power_det<- extend (int_final_det, along = 'Participant', n= 100)
pcurvedet_n100 <- powerCurve(power_det, test=fcompare(help.response~Condition), along='Participant')
pcurve_coh <- powerCurve(int_final_coh, test=fcompare(help.response~Condition), along='Participant')
plot(pcurvedet_n100)
plot(pcurve_coh)
```


#Multilevel Mediation analysis
Perspective taking
##Path a
```{r}

detach (package:lmerTest, unload=T)
library(lmerTest)
#Identify vs Imagine:path a
med.fit_0v2_zcp<- lmer(Perspective.response~dummy_est +dummy_img+(dummy_est +dummy_img||Participant), data= IPE.df)
step(med.fit_0v2_zcp)#remove dummy_est
##Final model
med.fit_0v2_final<- lmer(Perspective.response~dummy_est +dummy_img+(dummy_img|Participant), data= IPE.df)
anova(med.fit_0v2_zcp,med.fit_0v2_final, refit=F)
summary(med.fit_0v2_final)

#Estimate vs Imagine:path a
med.fit_1v2_zcp<- lmer(Perspective.response~dummy_ident +dummy_img +(dummy_ident +dummy_img||Participant), data= IPE.df)
step(med.fit_1v2_zcp)#retain all
##Final Model
med.fit_1v2_final<- lmer(Perspective.response~dummy_ident +dummy_img + (dummy_img|Participant), data= IPE.df) #remove dummy_ident singular fit
anova(med.fit_1v2_zcp,med.fit_1v2_final, refit=F)
summary(med.fit_1v2_final)
```
##Path b and c'
```{r}
#Identify vs Imagine:path b and c'
out.fit_0v2_zcp<- lmer(help.response~dummy_est +dummy_img +Perspective_C+(dummy_est +dummy_img +Perspective_C||Participant), data= IPE.df)
step(out.fit_0v2_zcp) #remove perspective_C
##Final model
out.fit_0v2_final<- lmer(help.response~dummy_est +dummy_img +Perspective_C+(dummy_est+dummy_img|Participant), data= IPE.df)
anova(out.fit_0v2_zcp,out.fit_0v2_final, refit=F)
summary(out.fit_0v2_final)

#Estimate vs Imagine:path b and c'
out.fit_1v2_zcp<- lmer(help.response~dummy_ident +dummy_img +Perspective_C+(dummy_ident +dummy_img +Perspective_C||Participant), data= IPE.df)
step(out.fit_1v2_zcp)
#Final model
out.fit_1v2_final<- lmer(help.response~dummy_ident +dummy_img +Perspective_C+(dummy_ident +dummy_img |Participant), data= IPE.df) #Perspective_C removed: smallest variance
out.fit_1v2_final<-update(out.fit_1v2_final, .~., start= getME(out.fit_1v2_final, 'theta')) #fitted after one refit.
summary(out.fit_1v2_final)#remove dummy_Ident
```
##Mediation model
```{r}
#Identify vs Imagine
med.out_0v2 <- mediate (med.fit_0v2_final, out.fit_0v2_final, treat='dummy_img', mediator = 'Perspective_C')
summary(med.out_0v2);plot(med.out_0v2)

#Estimate vs Imagine
med.out_1v2 <- mediate (med.fit_1v2_final, out.fit_1v2_final, treat='dummy_img', mediator = 'Perspective_C')
summary(med.out_1v2);plot(med.out_1v2)

#Exploratory Identify vs Estimate
med.out_0v1 <- mediate (med.fit_0v2_final, out.fit_0v2_final, treat='dummy_est', mediator = 'Perspective_C')
summary(med.out_0v1);plot(med.out_0v1)
```

#Multilevel moderated mediation
###Detail
```{r}
library(lmerTest)
detach (package:lmerTest, unload=T)
interaction.df$imgdet_int<- interaction.df$dummy_img*interaction.df$Detail_C
#Mediation effect across the two conditons
med.fit_det <- lmer (Perspective.response~dummy_img*Detail_C+(dummy_img+Detail_C|Participant) ,data= interaction.df)
out.fit_det<- lmer (help.response~dummy_img*Detail_C+Perspective_C+(dummy_img|Participant),data= interaction.df)
Mod.Med_Detest <- mediate(med.fit_det, out.fit_det, covariates = list(dummy_img = 0), treat="Detail_C", mediator="Perspective_C")
Mod.Med_Detimg <- mediate(med.fit_det, out.fit_det,covariates = list(dummy_img = 1), treat="Detail_C", mediator="Perspective_C")
#Moderated mediation analysis
med.fit_det2 <- lmer (Perspective.response~dummy_img+Detail_C+imgdet_int+(dummy_img+Detail_C|Participant) ,data= interaction.df)
out.fit_det2<- lmer (help.response~dummy_img+Detail_C+imgdet_int+Perspective_C+(dummy_img|Participant),data= interaction.df) 
med.out_det <- mediate (med.fit_det2, out.fit_det2, treat='imgdet_int', mediator = 'Perspective_C')
summary(Mod.Med_Detest);summary(Mod.Med_Detimg);summary(med.out_det)
summary(med.fit_det);summary(out.fit_det)
#used to plot path a 
est_detpersp<- lmer (Perspective.response~Detail_C+(Detail_C|Participant),data= subset(interaction.df,Condition=="Estimate"))
img_detpersp<- lmer (Perspective.response~Detail_C+(Detail_C|Participant) ,data= subset(interaction.df,Condition=="Imagine"))
summary(est_detpersp);summary(img_detpersp)
```

##Coherence
```{r}
library(lmerTest)
detach (package:lmerTest, unload=T)
#below only inlcude parsimonious model
interaction.df$imgcoh_int<- interaction.df$dummy_img*interaction.df$Coherence_C
#Mediation effect across the two conditons
med.fit_coh <- lmer (Perspective.response~dummy_img*Coherence_C+(dummy_img+Coherence_C|Participant),data= interaction.df)
out.fit_coh<- lmer (help.response~dummy_img*Coherence_C+Perspective_C+(dummy_img|Participant),data= interaction.df) 
Mod.Med_Cohest <- mediate(med.fit_coh, out.fit_coh, covariates = list(dummy_img = 0), treat="Coherence_C", mediator="Perspective_C")
Mod.Med_Cohimg <- mediate(med.fit_coh, out.fit_coh, covariates = list(dummy_img = 1), treat="Coherence_C", mediator="Perspective_C")
#Moderated mediation analysis
med.fit_coh2 <- lmer (Perspective.response~dummy_img+Coherence_C+imgcoh_int+(dummy_img+Coherence_C|Participant),data= interaction.df)
out.fit_coh2<- lmer (help.response~dummy_img+Coherence_C+Perspective_C+imgcoh_int+(dummy_img|Participant),data= interaction.df) 
med.out_coh <- mediate (med.fit_coh2, out.fit_coh2, treat='imgcoh_int', mediator = 'Perspective_C')
summary(Mod.Med_Cohest);summary(Mod.Med_Cohimg);summary(med.out_coh)
summary(med.fit_coh);summary(out.fit_coh)
#use to plot path a
est_cohpersp<- lmer (Perspective.response~Coherence_C+(Coherence_C|Participant),data= subset(interaction.df,Condition=="Estimate"))
img_cohpersp<- lmer (Perspective.response~Coherence_C+(Coherence_C|Participant),data= subset(interaction.df,Condition=="Imagine"))
summary(est_cohpersp);summary(img_cohpersp)
```
##Scene
```{r}
library(lmerTest)
detach (package:lmerTest, unload=T)
#below only inlcude parsimonious model
interaction.df$imgscene_int<- interaction.df$dummy_img*interaction.df$Scene_C
#Mediation effect across the two conditons
med.fit_scene <- lmer (Perspective.response~dummy_img*Scene_C+(dummy_img+Scene_C|Participant),data= interaction.df)
out.fit_scene<- lmer (help.response~dummy_img*Scene_C+Perspective_C+(dummy_img|Participant),data= interaction.df) 
Mod.Med_sceneest <- mediate(med.fit_scene, out.fit_scene, covariates = list(dummy_img = 0), treat="Scene_C", mediator="Perspective_C")
Mod.Med_sceneimg <- mediate(med.fit_scene, out.fit_scene, covariates = list(dummy_img = 1), treat="Scene_C", mediator="Perspective_C")
#Moderated mediation analysis
med.fit_scene2 <- lmer (Perspective.response~dummy_img+Scene_C+imgscene_int+(dummy_img+Scene_C|Participant),data= interaction.df)
out.fit_scene2<- lmer (help.response~dummy_img+Scene_C+Perspective_C+imgscene_int+(dummy_img|Participant),data= interaction.df) 
med.out_scene <- mediate (med.fit_scene2, out.fit_scene2, treat='imgscene_int', mediator = 'Perspective_C')
summary(Mod.Med_sceneest);summary(Mod.Med_sceneimg);summary(med.out_scene)
summary(med.fit_scene);summary(out.fit_scene)
#Use for SEs, a, c'
img_SP <- lmer (Perspective.response~dummy_est*Scene_C+(dummy_est+Scene_C|Participant),data= interaction.df)
img_SH<- lmer (help.response~dummy_est*Scene_C+Perspective_C+(dummy_est|Participant),data= interaction.df) 
summary(img_SP);summary(img_SH)
```
#Multilevel factor analysis
removed intrigued and intent.
Have a 2 factor model with distress and empathy
```{r}
emotion_num <- c(19,21,23,25,27,31,33,35,37,39)
emoFA.df<- data.frame ('Participants'=IPE.df$Participant, IPE.df[emotion_num])
mcfa_emotreact<- mcfa.input('Participants',emoFA.df)
twofactor <- 'Empathy =~ softhearted.response+warm.response+sympathetic.response+
                        compassionate.response+tender.response+moved.response; 
              Distress=~ troubled.response+distressed.response+disturb.response+worried.response'
result1_emotreact<- cfa(twofactor, sample.cov=mcfa_emotreact$pw.cov, sample.nobs=mcfa_emotreact$n-mcfa_emotreact$G )
summary(result1_emotreact,fit.measures=T, standardized=T)
twofactor_loading_emot<-lavPredict(result1_emotreact, newdata=emoFA.df)
emotreact.df<- IPE.df
emotreact.df <- cbind(emotreact.df, twofactor_loading_emot)
```

##Data preparation
```{r}
emotreact.df<- emotreact.df%>% 
                      mutate(
                        Empathy_C=group_center(Empathy, Participant),
                        Distress_C=group_center(Distress, Participant),
                        Empathy_M=means(Empathy, Participant),
                        Distress_M=means(Distress, Participant),
                        Empathy_MC= Empathy_M-mean(unique(emotreact.df$Empathy_M)),
                        Distress_MC= Distress_M-mean(unique(emotreact.df$Distress_M))
                        )

```

##2 factor models: Empathy MLM. 

###Empathy
```{r}
#identify as referece
emotreact.df$Condition <- relevel(emotreact.df$Condition, ref= 'Identify')
#Empathy
empathy_zcp<- lmer(help.response~Condition*(Empathy_C+Empathy_MC)+((dummy_est+dummy_img)*Empathy_C||Participant)+((dummy_est+dummy_img)*(Empathy_C+Empathy_MC)||Story_ID), data= emotreact.df)
empathy_step<- step(empathy_zcp) #keep  only dummy_img, dummy_est, Empathy_C in Participant, and empathy_MC in story
empathy_rm<- lmer(help.response~Condition*(Empathy_C+Empathy_MC)+(dummy_img+dummy_est+Empathy_C||Participant)+(Empathy_MC||Story_ID), data= emotreact.df)
empathy_rm<- update(empathy_rm, .~., start= getME(empathy_rm, 'theta'))
##Final model
empathy_final<- lmer(help.response~Condition*(Empathy_C+Empathy_MC)+(dummy_img+dummy_est+Empathy_C|Participant)+(Empathy_MC|Story_ID), data= emotreact.df)
empathy_final<- update(empathy_final, .~., start= getME(empathy_final, 'theta')) #3 refit 
anova(empathy_rm,empathy_final, refit=F)
anova(empathy_final, test='kenward-roger')
summary(empathy_final)

#identify as referece
emotreact.df$Condition <- relevel(emotreact.df$Condition, ref= 'Estimate')
#Empathy
empathy_zcp2<- lmer(help.response~Condition*(Empathy_C+Empathy_MC)+((dummy_ident+dummy_img)*Empathy_C||Participant)+((dummy_ident+dummy_img)*(Empathy_C+Empathy_MC)||Story_ID), data= emotreact.df)
empathy_step2<- step(empathy_zcp) #keep  only dummy_img, dummy_ident, Empathy_C in Participant, and empathy_MC in story
empathy_rm2<- lmer(help.response~Condition*(Empathy_C+Empathy_MC)+(dummy_img+Empathy_C||Participant)+(Empathy_MC||Story_ID), data= emotreact.df)
empathy_rm2<- update(empathy_rm, .~., start= getME(empathy_rm, 'theta'))
##Final model
empathy_final2<- lmer(help.response~Condition*(Empathy_C+Empathy_MC)+(dummy_img+Empathy_C|Participant)+(Empathy_MC|Story_ID), data= emotreact.df)
empathy_final2<- update(empathy_final, .~., start= getME(empathy_final, 'theta')) #1 refit 
anova(empathy_rm2,empathy_final2, refit=F)
anova(empathy_final2, test='kenward-roger')
summary(empathy_final2)
```

#####plots
```{r}
emtrends(empathy_opt, pairwise~Condition, var='Empathy_MC',adjust='none')

sd<-sd(unique(emotreact.df$Empathy_MC))
m<-mean(unique(emotreact.df$Empathy_MC))
m-sd;m;m+sd
ggpredict(empathy_final2, c("Condition","Empathy_MC [-1.04,0,1.04]"))%>% plot()
ggpredict(empathy_final2, c("Empathy_MC[-1.04,0,1.04]","Condition"))%>% plot()
plot_model(empathy_final2, type='re')
```
#### power analysis
based on ref group as estimate and no random effect
```{r}
empathy_power<- lmer(help.response~(dummy_img+dummy_ident)*(Empathy_C+Empathy_MC)+(dummy_img+Empathy_C|Participant)+(Empathy_MC|Story_ID), data= emotreact.df)
empathy_power<- update(empathy_power, .~., start= getME(empathy_power, 'theta')) #4 refit
empathy_norand<- lmer(help.response~(dummy_ident+dummy_img)*(Empathy_C+Empathy_MC)+(1|Participant)+(1|Story_ID), data= emotreact.df)

model_test<- extend (empathy_power, along = 'Participant', n= 200)
p_curve_n200 <- powerCurve(model_test, test=fixed("dummy_img:Empathy_MC", "z"), along='Participant')
p_curve_norand<-powerCurve(empathy_final2_2fact_ref1_norand, test=fixed("dummy_img:Empathy_MC", "z"), along='Participant')
plot(p_curve_norand);plot(p_curve_n200)
```

##Distress
```{r}
#identify as referece
emotreact.df$Condition <- relevel(emotreact.df$Condition, ref= 'Identify')
#Distress
distress_zcp0<- lmer(help.response~Condition*(Distress_C+Distress_MC)+((dummy_est+dummy_img)*Distress_C||Participant)+((dummy_est+dummy_img)*(Distress_C+Distress_MC)||Story_ID), data= emotreact.df)
distress_step0<-step(distress_zcp0) #remove all from story ID apart from dummy_img:distress_C, retain only dummy_est, dummy_ident AND Distress_C
distress_rm<- lmer(help.response~Condition*(Distress_C+Distress_MC)+(dummy_est+Distress_C+dummy_img||Participant)+(dummy_img:Distress_C||Story_ID), data= emotreact.df)
distress_rm<- update(distress_rm, .~., start= getME(distress_rm, 'theta')) #5 refit 
#final
distress_opt0<- lmer(help.response~Condition*(Distress_C+Distress_MC)+(dummy_est+Distress_C+dummy_img|Participant)+(1|Story_ID), data= emotreact.df) #dummy_img:distress_C singular fit remove
distress_final<- lmer(help.response~Condition*(Distress_C+Distress_MC)+(dummy_est+dummy_img|Participant)+(1|Story_ID), data= emotreact.df) #convergnce failure remove smallest parameter distress_C
distress_final<- update(distress_final, .~., start= getME(distress_final, 'theta')) #2 refit
summary(distress_final)
anova(distress_final, test='kenward-roger')
```













